Rapid, (semi-?)Supervised Generation of Novel Percussive Sounds With A Tractable Virtual Synthesizer

### 2020-01-01 NIME_PAPER/paper.tex
Updates from Overleaf

\todo[inline, color=green!30]{I think it might be worthwhile to point out that our work has great potential for live performances, especially compared to other work, would that be appropriate for a scientific paper? should it be done here or in related work?}
\subsection{Methodology}
Towards our goal of generating original audio, we found the proper implementation of 2 major components to be crucial:
\begin{itemize}
    \item \textit{Virtual Synthesizer}:A flexible, deterministic, and tractable generator which can create audio. The core of our implementation made use of pippi, \footnote{https://github.com/luvsound/pippi} a fast, offline focused python DSP library with a C backend. We additionally used the scipy \cite{jones2001scipy} library a few audio effects that we found lacking in pippi. 
    \item \textit{Virtual Ear}: An ear that returns an evaluation of an audio sample; estimating the effectiveness of an audio sample's fulfillment of a producers requirements. The implementation and training of the ear guides the generation process towards a desired path. We used a labeled set of percussive and non-percussive audio files as training data to try a few different implementations of an ear, settling on a combination of a Convolutional Neural Net (CNN) model and a custom envelope detection algorithm as our "virtual drum detector ear". \\
\end{itemize}
Following the Unix Philosophy \cite{gancarz2003linux}, our components are designed with modularity and parallelizability in mind. This allows each component to be debugged, modified and improved without requiring modifications in other components; additionally, increasing the scalability and speed of experiments.
Section \ref{impl} contains further discussion of the components as well as the code that glues the project together can be found in .\\ 
While the main focus of this project is the generation of novel percussive sounds, our methodology indicates promising results with regards to creation of new presets for any virtual synth without the need for a-priori knowledge of the functions of its parameters (i.e the effect of parameter modulation on the sonic output). We also demonstrate the viability of a few lesser explored avenues for the purposes of audio synthesis and Music Information Retrieval (MIR), notably:
\begin{enumerate}[label=\roman*]
\item Heuristic search methods for the creation of new presets for virtual synthesizers. More concretely, we observed that given a virtual ear which could reliably score pieces of audio based on its resemblance to a desired category (e.g:kicks,snares,piano), we were able to rapidly search the parameters of a virtual synthesizer and create numerous parameter-sets (i.e presets) which resemble our desired category of sounds.
\item The viability of virtual synthesizers based on Digital Signal Processing (DSP) methods for fast, unsupervised creation of novel audio, discussed in more detail in section \ref{related}. \\
\end{enumerate}

>>>>

\todo[inline, color=green!30]{I think it might be worthwhile to point out the potential in our work for live performance, compared to other works which use 3rd party VSTs, require pre-training and user interaction, would that be appropriate for a scientific paper? should it be done here or in related work?}
\subsection{Methodology}
Towards our goal of generating original audio, we found the proper implementation of 2 major components to be crucial:
\begin{itemize}
    \item \textit{Virtual Synthesizer}:A flexible, deterministic, and tractable generator which can create audio. The core of our implementation made use of pippi, \footnote{https://github.com/luvsound/pippi} a fast, offline focused python DSP library with a C backend. We additionally used the scipy \cite{jones2001scipy} library a few audio effects that we found lacking in pippi. 
    \item \textit{Virtual Ear}: An ear that returns an evaluation of an audio sample; estimating the effectiveness of an audio sample's fulfillment of a producers requirements. The implementation and training of the ear guides the generation process towards a desired path. We used a labeled set of percussive and non-percussive audio files as training data to try a few different implementations of an ear, settling on a combination of a Convolutional Neural Net (CNN) model and a custom envelope detection algorithm as our "virtual drum detector ear". \\
\end{itemize}
Following the Unix Philosophy \cite{gancarz2003linux}, our components are designed with modularity and parallelizability in mind. This allows each component to be debugged, modified and improved without requiring modifications in other components; additionally, increasing the scalability and speed of experiments.
Section \ref{impl} contains further discussion of the components as well as the code that glues the project together can be found in .\\ 
While the main focus of this project is the generation of novel percussive sounds, our methodology indicates promising results with regards to creation of new presets for any virtual synth without the need for a-priori knowledge of the functions of its parameters (i.e the effect of parameter modulation on the sonic output). We also demonstrate the viability of a few lesser explored avenues for the purposes of audio synthesis and Music Information Retrieval (MIR), notably:
\begin{enumerate}[label=\roman*]
\item Heuristic search methods for the creation of new presets for virtual synthesizers. More concretely, we observed that given a virtual ear which could reliably score pieces of audio based on its resemblance to a desired category (e.g:kicks,snares,piano), we were able to rapidly search the parameters of a virtual synthesizer and create numerous parameter-sets (i.e presets) which resemble our desired category of sounds.
\item The viability of virtual synthesizers based on Digital Signal Processing (DSP) methods for fast, unsupervised creation of novel audio, discussed in more detail in section \ref{related}. \\
\end{enumerate}
